Rigidity of Expectations: Additional Evidence from Density Forecasts of the Inflation by Professionals and Households

### 2019-12-01 paper/InfVar.tex
small typo in abstract.

	\begin{abstract}
	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark. This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors. Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments. This is a natural extension of \citet{coibion2012can}, which examines different moments separately. Also, motivated by the time-varying pattern of the uncertainty observed from the surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility. These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness than the in baseline setting. It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.   
	\end{abstract}

>>>>

	\begin{abstract}
	Density forecasts of macroeconomic variables provide one additional moment restriction, uncertainty, for testing and exploring the implications of theories about how people form expectations differently from full-information rationality benchmark. This paper first documents the persistent dispersion in inflation uncertainty of professionals and households, and how it conveys different information from the widely used proxies to uncertainty such as cross-sectional disagreement and forecast errors. Second, utilizing the panel data structure of both surveys, I provide additional reduced-form test results as well as structural estimates for each particular theory of ``irrational expectation'' by jointly accounting for its predictions for different moments. This is a natural extension of \citet{coibion2012can}, which examines different moments separately. Also, motivated by the time-varying pattern of the uncertainty observed from surveys, I extend their work to allow for an alternative inflation process featuring stochastic volatility. These extensions allow me to match the joint dynamics of inflation and forecast moments in a better degree of fitness. It also illustrates how incorporating higher moments from survey data helps understand both the expectation formation mechanisms and inflation dynamics.   
	\end{abstract}
